\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}

\geometry{a4paper, margin=1in}

\title{\textbf{Engagement Activities of Stakeholders in Healthcare}}
\author{Heider Jeffer}
\date{}

\begin{document}
	
	\maketitle
	
	\section*{Stakeholders and Their Engagement Activities}
	
	\subsection*{Patients}
	\begin{itemize}[label=--]
		\item \textbf{Participation in Care}: Engaging actively in their own healthcare processes, such as attending appointments and following treatment plans. \\ \textit{(Base engagement: 0.6)}
		\item \textbf{Feedback and Communication}: Providing input on care experiences and maintaining open communication with healthcare providers. \\ \textit{(Base engagement: 0.5)}
		\item \textbf{Health Literacy}: Understanding health information to make informed decisions. \\ \textit{(Base engagement: 0.55)}
		\item \textbf{Preventative Care}: Taking measures to prevent illnesses, such as vaccinations and regular screenings. \\ \textit{(Base engagement: 0.7)}
	\end{itemize}
	
	\subsection*{Doctors}
	\begin{itemize}[label=--]
		\item \textbf{Direct Care Delivery}: Providing hands-on medical treatment and care to patients. \\ \textit{(Base engagement: 0.8)}
		\item \textbf{Professional Development}: Participating in training, education, and certifications to enhance skills. \\ \textit{(Base engagement: 0.7)}
		\item \textbf{Collaboration}: Working with other doctors, nurses, and stakeholders to improve patient outcomes. \\ \textit{(Base engagement: 0.75)}
		\item \textbf{Research and Advocacy}: Contributing to medical research and advocating for better healthcare policies. \\ \textit{(Base engagement: 0.65)}
	\end{itemize}
	
	\subsection*{Nurses}
	\begin{itemize}[label=--]
		\item \textbf{Patient-Centered Care}: Providing compassionate and personalized care to patients. \\ \textit{(Base engagement: 0.75)}
		\item \textbf{Coordination and Communication}: Ensuring smooth communication between healthcare teams and managing patient care coordination. \\ \textit{(Base engagement: 0.8)}
		\item \textbf{Professional Development}: Engaging in training and certifications to enhance nursing expertise. \\ \textit{(Base engagement: 0.7)}
		\item \textbf{Community Involvement}: Participating in public health initiatives and local healthcare outreach. \\ \textit{(Base engagement: 0.6)}
	\end{itemize}
	
	\subsection*{Administrators}
	\begin{itemize}[label=--]
		\item \textbf{Operational Oversight}: Managing daily operations in healthcare facilities to ensure efficiency. \\ \textit{(Base engagement: 0.5)}
		\item \textbf{Stakeholder Coordination}: Facilitating collaboration among patients, providers, and other stakeholders. \\ \textit{(Base engagement: 0.45)}
		\item \textbf{Strategic Planning}: Developing long-term goals and plans for healthcare organizations. \\ \textit{(Base engagement: 0.55)}
		\item \textbf{Data-Driven Decision-Making}: Using data analytics to inform decisions and improve outcomes. \\ \textit{(Base engagement: 0.6)}
	\end{itemize}
	
\end{document}
